---
title: "rwa_data_analysis"
author: "VM"
date: "12/11/2020"
output: html_document
---

#Load libraries and read data
```{r}
library(tidyverse) 
rwa_data <- read_csv("~/dirty_data_project/task5/clean_data/clean_rwa_data.csv")
```
#What’s the average RWA score for each gender?
```{r}
rwa_data %>% 
  select(q3:q22, gender) %>% 
  drop_na(gender) %>% 
  group_by(gender) %>% 
  summarise(avg_rwa = mean(q3:q22, na.rm = TRUE))
  
```
#What’s the average RWA score for left handed people vs. right handed people.
```{r}
rwa_data %>% 
  select(q3:q22, hand) %>% 
  drop_na(hand) %>% 
  filter(hand != "both") %>% 
  group_by(hand) %>% 
  summarise(avg_rwa = mean(q3:q22, na.rm = TRUE))
```
#What’s the average family size for each type of childhood?
```{r}
rwa_data %>% 
  select(familysize, urban) %>% 
  drop_na(urban) %>% 
  group_by(urban) %>% 
  summarise(avg_family = mean(familysize, na.rm = TRUE))
```
#What’s the average time to take the test for each education level?
```{r}
time_education <- rwa_data %>% 
  select(e3:e22, education) %>% 
  drop_na(education) %>% 
  group_by(education) %>% 
  summarise(avg_time = mean(e3:e22, na.rm = TRUE))

time_education
```
#Create a plot of results of question 4.
```{r}
ggplot() +
  geom_col(data = time_education, aes(x = education, y = avg_time), colour = "black", 
           fill="sky blue") +
  labs(title = "Plot of average time spent on rwa over education level") +
  theme_classic()
```
#What’s the average RWA score for people aged
Under 18
18 to 25
26 to 40
41 to 60
Over 60
```{r}
rwa_data %>% 
  mutate(age_categories = case_when(age < 18 ~ "under 18",
                                    age >= 18 & age < 25 ~ "18 to 25",
                                    age > 26 & age < 40 ~ "26 to 40",
                                    age > 41 & age < 60 ~ "41 to 60",
                                    age >= 60 ~ "over 60")) %>% 
  select(age_categories, q3:q22) %>% 
  drop_na(age_categories) %>% 
  group_by(age_categories) %>% 
  summarise(avg_rwa = mean(q3:q22, na.rm = TRUE))
```

