---
title: "decathlon_data_analysis"
author: "VM"
date: "12/11/2020"
output: html_document
---

#Load libraries and data
```{r}
library(tidyverse)
decathlon_data <- read_csv("~/dirty_data_project/task1/clean_data/decathlon_clean_data.csv")
```
#Who had the longest long jump seen in the data?
```{r}
decathlon_data %>% 
  select(names, long_jump, rank) %>% 
  slice_max(long_jump, n = 3)

```
#What was the average 100m time in each competition?
```{r}
decathlon_data %>% 
  select(run_100m, competition) %>% 
  group_by(competition) %>% 
  summarise(avg_run100m = mean(run_100m))
```
#Who had the highest total points across both competitions?
```{r}
decathlon_data %>% 
  select(names, points, competition) %>% 
  group_by(competition) %>% 
  slice_max(points)
```
#What was the shot-put scores for the top three competitors in each competition?
```{r}
decathlon_data %>% 
  select(shot_put, competition) %>% 
  group_by(competition) %>% 
  slice_max(shot_put, n = 3)
```
#What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?
```{r}
decathlon_data %>% 
  select(points, run_400m) %>% 
  filter(run_400m < 50) %>% 
  summarise(avg_points = mean(points))

decathlon_data %>% 
  select(points, run_400m) %>% 
  filter(run_400m > 50) %>% 
  summarise(avg_points = mean(points))
```


